An Authoritative Adventure

### 2020-07-26 article.tex
Fixed up the background "paper image" option so that it defaults to the standard one without having to be explicitly defined in the document
Added the "ornamentedbox" and table environment for doing tables like "spellcaster". Attempted adaptation from https://tex.stackexchange.com/a/501736/2575, can't move everything to the dndtable.sty file due to pgfkeys errors with the textcolorbox skin defs.

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{graphicx}
\usepackage{titling}

@@

% Override the default background "paper" image with an alternate one.
\paperimage{img/paper-article}

@@

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{graphicx}
\usepackage{titling}
\usetikzlibrary{intersections}

@@

% Override the default background "paper" image with an alternate one.
\SetPaperImage{img/paper-article}

@@

% Code from Loop Space: <https://tex.stackexchange.com/a/26386/73317>
\makeatletter
\tikzset{
  use path for main/.code={%
    \tikz@addmode{%
      \expandafter\pgfsyssoftpath@setcurrentpath\csname tikz@intersect@path@name@#1\endcsname
    }%
  },
  use path for actions/.code={%
    \expandafter\def\expandafter\tikz@preactions\expandafter{\tikz@preactions\expandafter\let\expandafter\tikz@actions@path\csname tikz@intersect@path@name@#1\endcsname}%
  },
  use path/.style={%
    use path for main=#1,
    use path for actions=#1,
  }
}
\makeatother
% End of the code from Loop Space

% Ornamented box content from: https://tex.stackexchange.com/a/501736/2575
% TODO: Work out how to get the rest of the content from here into the dndtable.sty
%       file, which causes errors like:
%         ! Package pgfkeys Error: I do not know the key '/tcb/skinfirst'
\tikzset{ornamented frame inner/.style={color=ornamentedFrameInner,
                                        line width=2pt},
         ornamented frame outer/.style={color=ornamentedFrameOuter,
                                        line width=3pt}}

\tcbsubskin{ornamented}{empty}{
  skin first=ornamented, skin middle=ornamented, skin last=ornamented,
  title engine=standard,
  frame code={
    % Account for the line widths in order not to draw beyond the bounding
    % box---except for a few very small details for which this is intentional.
    \coordinate (north west) at ([shift={(-1.5pt,9.5pt)}]frame.north west);
    \coordinate (north east) at ([shift={(1.5pt,9.5pt)}]frame.north east);
    \coordinate (south east) at ([shift={(1.5pt,-9.5pt)}]frame.south east);
    \coordinate (south west) at ([shift={(-1.5pt,-9.5pt)}]frame.south west);
    %
    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
                                  34pt/south west, -34pt/south east} {
      \fill[color=ornamentedFrameOuter]
        ([xshift=\xoffset]\point) circle[radius=2.5pt];
    }
    %
    \path[name path=ornament 1]  ([yshift=-4pt]north west)
      [rounded corners=0.5pt] -- ++(23pt,0)
      [rounded corners=2pt]   -- ++(3pt,-4pt)
                              -- ([shift={(-26pt,-8pt)}]north east)
      [rounded corners=0.5pt] -- ++(3pt,4pt)
      [rounded corners=4pt]   -- ([yshift=-4pt]north east)
                              -- ([yshift=4pt]south east)
      [rounded corners=0.5pt] -- ++(-23pt,0)
      [rounded corners=2pt]   -- ++(-3pt,4pt)
                              -- ([shift={(26pt,8pt)}]south west)
      [rounded corners=0.5pt] -- ++(-3pt,-4pt)
      [rounded corners=4pt]   -- ([yshift=4pt]south west)
                              -- cycle;
    %
    \path[rounded corners=0.5pt, name path=ornament 2]
                                 ([yshift=-20pt]north west)
                              -- ++(-4pt,3pt)
                              -- ++(0,4pt)
               to[out=0, in=-90] ([shift={(8pt,0pt)}]north west)
                              -- ([shift={(34pt,0pt)}]north west)
                              -- ([shift={(-8pt,0pt)}]north east)
             to[out=-90, in=180] ([shift={(4pt,-13pt)}]north east)
                              -- ++(0,-4pt)
                              -- ++(-4pt,-3pt)
                              -- ([yshift=20pt]south east)
                              -- ++(4pt,-3pt)
                              -- ++(0,-4pt)
              to[out=180, in=90] ([shift={(-8pt,0pt)}]south east)
                              -- ([shift={(8pt,0pt)}]south west)
                to[out=90, in=0] ([shift={(-4pt,13pt)}]south west)
                              -- ++(0,4pt)
                              -- ++(4pt,3pt)
                              -- cycle;
    %
    \draw[ornamented frame outer, use path=ornament 1,fill=white];
    \draw[ornamented frame outer, use path=ornament 2];
    \draw[ornamented frame inner, use path=ornament 1];
    \draw[ornamented frame inner, use path=ornament 2];
    %
    \foreach \xoffset/\point in {34pt/north west, -34pt/north east,
                                 34pt/south west, -34pt/south east} {
      \fill[color=ornamentedFrameInner]
        ([xshift=\xoffset]\point) circle[radius=2pt];
    }
  }
}

% These parameters---especially those related to geometry---are better located
% here in a style than in the subskin definition (see the Subskins section of
% the tcolorbox manual).
\tcbset{ornamented/.style={skin=ornamented, coltitle=black, toptitle=5pt,
                           % Reserve vertical space for the decorations---space
                           % that disappears at page breaks.
                           beforeafter skip=28pt}
}

@@

The |ornamentedtabular| allows tables similar to those used for spellcasters
(see over page).

\begin{figure*}[h]
\begin{ornamentedtabular}{cclccccccccccc}[title={The Full Caster}]
  & & & & & \multicolumn{9}{c}{\thead{--- Spell Slots per Spell Level ---}} \\
  \textbf{Level} & \textbf{\makecell{Proficiency\\Bonus}} & \textbf{Features} & \textbf{\makecell{Cantrips\\Known}} & \textbf{\makecell{Spells\\Known}} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
  1st  & +2 & Feature & 3 & 4  & 2 & — & — & — & — & — & — & — & — \\
  2nd  & +2 & Feature & 3 & 4  & 3 & — & — & — & — & — & — & — & — \\
  3rd  & +2 & Feature & 4 & 4  & 4 & 2 & — & — & — & — & — & — & — \\
  4th  & +2 & Feature & 4 & 5  & 4 & 3 & — & — & — & — & — & — & — \\
  5th  & +3 & Feature & 4 & 6  & 4 & 3 & 2 & — & — & — & — & — & — \\
  6th  & +3 & Feature & 4 & 7  & 4 & 3 & 3 & — & — & — & — & — & — \\
  7th  & +3 & Feature & 4 & 8  & 4 & 3 & 3 & 1 & — & — & — & — & — \\
  8th  & +3 & Feature & 4 & 9  & 4 & 3 & 3 & 2 & — & — & — & — & — \\
  9th  & +4 & Feature & 4 & 10 & 4 & 3 & 3 & 3 & 1 & — & — & — & — \\
  10th & +4 & Feature & 5 & 11 & 4 & 3 & 3 & 3 & 2 & — & — & — & — \\
  11th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
  12th & +4 & Feature & 5 & 12 & 4 & 3 & 3 & 3 & 2 & 1 & — & — & — \\
  13th & +4 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
  14th & +5 & Feature & 5 & 13 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & — & — \\
  15th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
  16th & +5 & Feature & 5 & 14 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & — \\
  17th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1 \\
  18th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1 \\
  19th & +6 & Feature & 4 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1 \\
  20th & +6 & Feature & 5 & 15 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1 \\
\end{ornamentedtabular}
\end{figure*}
